A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-01-02 main.tex
error from \subsection*{Cutoff Finder Core Engine}
\subsection*{Statistical Consideration}

>>>>

\subsection*{Cutoff Finder Core Engine}

\subsection*{Statistical Consideration}

\subsection*{Biomarker Selection}

Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
